I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-24 Paper/Paper_noProof.tex
table 6

\vspace{-0.4cm}
\begin{figure}[h!]
	\centering
\begin{tikzpicture}
	\begin{axis}[width=10cm,height=5cm,
		xlabel={},
		ylabel={},
		title={runtime (seconds per node)},
		legend pos=north west,
		ymin=0,
		xtick={1,2,3,4,5}, 
		xticklabels={$5\times 100$, $8\times 100$, $5\times 200$, $8\times 200$, $6\times 500$},
		]

>>>>

\vspace{-0.4cm}
\begin{figure}[h!]
	\centering
\begin{tikzpicture}
	\begin{axis}[width=10cm,height=5cm,
		xlabel={},
		ylabel={},
		title={runtime (seconds per node)},
		legend pos=south east,
		ymin=0,
		xtick={1,2,3,4,5}, 
		xticklabels={$5\times 100$, $8\times 100$, $5\times 200$, $8\times 200$, $6\times 500$},
		]
